Comments on the revised version

### 2018-01-12 paper/paper.tex
fixes

Let us emphasize the main results of this study: While the First-Come,
First-Serve approach to minimizing the waiting times is a common default
strategy, it can definitively be outperformed. We show how to automate selection
of a good alternative policy in two cases (depending on whether a simulator is
available or not), and provide the difference in performance to be expected
between both situations.

@@

Let $l(\Delta_t)$ denote the number of jobs \textit{submitted} during the
period $\Delta_t$ ($0 \le t $), and $P_i$ ($1 \le i \le 12$) one reordering
policy (defined in Section~\ref{subsec:policies}). The cost of policy $P_i$
during period $\Delta_t$ is defined as:
%
\begin{equation} \label{eq:cost-exact} w(t;P_i) = \sum_{j=1}^{l(\Delta_t)}
\mbox{Wait}_j^{P_i} \end{equation}
%
where $\mbox{Wait}_j^{P_i}$ denotes the estimate provided by the simulator of
the waiting time for job $j$ according to policy $P_i$. The estimation of the
cost of a policy over all the periods preceding the current period can then be
defined as:
%
\begin{equation} \label{eq:tot-cost-exact} w(\rightarrow T;P_i) =
\sum_{t=0}^{T-1} \lambda^{T-1-t} w(t;P_i) \end{equation}
%
where $\lambda \in [0,1]$ is a decaying discount factor that can be used to
privilege recent history (\textit{i.e.} recent periods). The above formulation
is general and covers several possible situations : From stationary job
distributions where $\lambda$ can be set to 1 to non-stationary distributions
where the more recent history has to be privileged. As explained in Section
6.1, in our experiments $\lambda$ is set to 1 as the distributions considered
are stationary but the reader has to bear in mind that our framework can be use
on different distributions by resorting to different values of lambda that can
be set by cross-validation.

>>>>

Let us emphasize the main results of this study. We show how to select a good
alternative to the First-Come, First-Serve policy in an online manner. We
present two automated methods for selecting a good alternative policy in two
cases (depending on whether a simulator is available or not), and provide the
difference in performance to be expected between both situations.

@@

Let $l(\Delta_t)$ denote the number of jobs \textit{submitted} during the
period $\Delta_t$ ($0 \le t $), and $P_i$ ($1 \le i \le 12$) one reordering
policy (defined in Section~\ref{subsec:policies}). The cost of policy $P_i$
during period $\Delta_t$ is defined as:
%
\begin{equation} \label{eq:cost-exact} w(t;P_i) = \sum_{j=1}^{l(\Delta_t)}
\mbox{Wait}_j^{P_i} \end{equation}
%
where $\mbox{Wait}_j^{P_i}$ denotes the estimate provided by the simulator of
the waiting time for job $j$ according to policy $P_i$. The estimation of the
cost of a policy over all the periods preceding the current period can then be
defined as:
%
\begin{equation} \label{eq:tot-cost-exact} w(\rightarrow T;P_i) =
\sum_{t=0}^{T-1} \lambda^{T-1-t} w(t;P_i) \end{equation}
%
where $\lambda \in [0,1]$ is a decaying discount factor that can be used to
privilege recent history (\textit{i.e.} recent periods). The above formulation
is general and covers several possible situations : From stationary job
distributions where $\lambda$ can be set to 1 to non-stationary distributions
where the more recent history has to be privileged. As explained in Section
6.1, in our experiments $\lambda$ is set to 1 as the distributions considered
are stationary but the reader has to bear in mind that our framework can be use
on different distributions by resorting to different values of $\lambda$ that can
be set by cross-validation.

### 2018-01-12 paper/revision.tex
fixes

\title{Major revision comments.}

@@

@@

@@

This is indeed a mistake on our part which made the way to the final version,
this is now corrected. The article is "Tuning Backfilling Queues" from JSSPP17.\\

@@

\textbf{Altogether, the reviewer believes that an experimental study with so
many design problems is not relevant to the readers of TDPS. }

\textbf{The reviewer does not see how the authors can overcome these
shortcomings even in a major revision and therefore suggest rejection of the
manuscript.}

@@

\textbf{Previous publications explain that studies using traces suffer from
fill-ins in the starting period and from draining in the final period. The
authors mention this problem but do not discuss their impact and strategies to
avoid these problems although other publications present such strategies.
Previous studies have described that the KTH trace is hardly comparable with
other traces due to a specific acceptance policy. The authors do not discuss
this problem. The authors use either 1 week or 1 day feedback justifying their
choices with the periodicity of the traces. Although such approach is
reasonable, it is a hypothesis and requires validation by using other feedback
periods as well and comparing the results. }

@@

@@

We added two figures to illustrate the algorithms.\\

\textbf{Since the journal provides a platform for supplemental material, the
reviewer does not understand why readers must contact the authors by email to
obtain data to reproduce the study.  }

As previously concerning the missing reference, this was inadvertent on our
part! This is fixed in the major revision. Apologies for this error.

@@

@@

The need for more careful framing of the goals of the study was stressed by all
reviewers. Accordingly, we made the scope of the study more clear and changed
the title, to "Online Tuning of EASY-Backfilling using Queue Reordering
Policies."\\

@@

\end{enumerate}
Thank you for your suggestions, we had not come across these papers! There are indeed very related to our effort.

@@

We did add a basic description of the setting in the description.\\

\textbf{Section 3.1 notation - intuitively p could represent processors just as
well as processing time, so I would suggest $t_i$ for time and $p_i$ for
processors.  Similarly, in Section 4.1 I for one would find the names more
intuitive with SJF/LJF instead of SPF/LPF (shortest/longes job first) SPF/LPF
instead of SQF/LQF (smallest/largest processors first) expansion factor is
often called slowdown area is often called total resources}

We agree that $p_i$ is not very intuitive, but for lack of a standard we chose
to use notation from scheduling theory.  In face of the many possible acronyms,
we chose to rather be consistent with the $p_i$ and $q_i$ notation - SPF ist
smallest $p_i$ first and SQF is smallest $q_i$ first..  We added the remark
concerning the total resources and the expansion factor. This notation comes
from the "Characterization of backfilling strategies for parallel job
scheduling" article, where the authors call Expansion Factor the value of the
slowdown where the upper bound on the running-time is used.\\

@@

We agree that this design choice can be discussed. Our decision to divide
makes the study more realistic with respect to the cases where simulations are
expensive(which is most large systems).  Indeed, the more realistic simulations
are, the more time they take. For example, precise simulation frameworks such
as SimGrid/Batsim have high runtimes, and simulating the history of the whole
system every period is prohibitive if the network topology and/or multiple
resource constraints are used. As for discounting - it can indeed be used
in both cases.\\

@@

We do agree that this does not change the estimate - the point of adding 
this noise was to show that the sample size is not prohibitive in practice.
Indeed, we learn the policy almost as fast with this noise, which
motivates the use of the technique in real-world cases. The point of this noise
is really to compare the difference in the shapes of the two green curves
in Figure 3.\\

@@

You are right - and we made this point clear in the text.\\

@@

Doing this would drown the point in the author's opinion. We agree it is an
interesting point - we now refer to our previous publication 'Tuning
Backfilling Queues'(JSSPP17), which was inadvertently ommited from the related
works of the first submission.\\

  \textbf{Section 6.3.2 FCFS vs. Random: you justify the result be a conjecture that jobs do not pile up in the queue.  you should verify this by counting the jobs int he queue in the simulation.}

We aggree that this conjecture is not warranted - we removed it in the revision.
We do have plans to explore this aspect for a future publication where the
discussion will be more appropriate.\\

@@

Done, thanks you for the suggestion.\\

@@

We changed the experimental protocol to use leave-one-out cross validation,
which did improve the bandit results. The selected exploration rate was 0.1 for
all traces, although it is not the best choice for all of them. (see the new
Table 2) The choice of a fixed exploration rate is one of simplicity - while
decaying exploration does provide better performance, it is also harder to
tune.\\

@@

This is corrected in the major revision - we inadvertently ommited this
when preparing the submission. The reference is 'Tuning Backfilling Queues'(JSSPP17).\\

@@

We incorporated these changes and thank the reviewer for their detailed read.\\

@@

We do agree with the reviewer that in order to really motivate the use of
bandit/resimulation aproaches, one should compare the performance of static
policies, say using leave-one-trace-out cross validation, to the performance of
the adaptive variants, using leave-one-trace-out cross validation for their
hyperparameters.
However, this work does not aim to underline the necessity of the bandit
approach (the title has been changed and the introduction modified in the major
revision to reflect this better). Rather, we try to show its advantages,
feasibility and limitations. 
There are two main reasons for not trying to be too demonstrative of the superiority
of the adaptive approach using our hypotheses.

First, this study uses a limited amount of workload logs. In consequence, the
process of comparing the adaptive (hyperparameter-cross-validated) choice to
the static (cross-validated in the set of fixed policies) choice would not be
really conclusive.  Indeed, the more workload logs are presented, the more
diversity is present and the more adaptation is necessary.
Second, we use a simplistic simulation model. In this model, we do make
machines *more* similar to each other by neglecting topological differences. It
can be reasonably expected that differences between systems should *increase*
rather than decrease, when moving away from a simplistic model to the real
systems.
We modified the present experiments to use leave-one-out cross
validation in the hyperparameter selection, and made the reasons for this
choice of experimental protocol clearer in the text.
We are preparing a subsequent study using an approach closer to what you
describe, in which we greatly increase the number of workload logs used.\\

\textbf{The authors assume +/-20% noise in the simulation running in the
proposed strategy. However, the reason why this assumption is suitable is not
presented. The authors should discuss the noise of 20% is suitable to represent
real world jobs.}

A justification was indeed missing, this value is taken as to be sufficiently
larger than values previously reported, see e.g. Batsim: a Realistic
Language-Independent Resources and Jobs Management Systems Simulator which
reports 2 percent variations of the simulated metric compared to the metric on
the real systems. We added this remark to the text.\\

@@

We incorporated these changes and thank the reviewer for their detailed read.\\

>>>>

\title{Comments on the revised version}

@@

Let us first sincerely thank the reviewers for their relevant and in-depth
remarks. Their comments helped us to clarify the focus of this work, which
lead to restructure the evaluation procedure to some extent. As part of these
modifications, we changed the title to: "Online Tuning of EASY-Backfilling
using Queue Reordering Policies". It better reflects the main goal, which is
not to advocate bandit strategies, but rather to study their feasibility, and
to show where the tradeoff is compared to using simulations for tuning the
algorithms. We hope this revised version may now be considered for publication. 
We detail our answers to rewiewer's comments (bold).

@@

General comments: Our scope in this work is is not to advocate particular scheduling strategies (Bandit), but rather to study their feasibility, 
and to show where the tradeoff is compared to using simulations for tuning the algorithms. 
We are aware that is it not so common in our field where the classical approach is to formalize an hypothesis and to assess it by experiments. 
The methodology that we propose here is to consider the 12 most popular (and efficient) reordering policies and to study their behavior.
In the mean time, this also leads to figure out at the end if we can select the best ones.
This methodology is closer to an empiristic study that are common in other fields.
We added a brief justification at the end of the introduction.
The reason why we have chosen this way was because it is very difficult to identify a priori what is the best policy and assess it. 
Our attempt was to consider all possible policies. 
\medskip

We answer below more specific points:

We focus in this paper on average waiting time. We have considered other objectives like bounded slow-down.
This choice simply reflects the view of the users. Other metrics are indeed possible,
and our method is agnostic to this choice.

We agree that thresholding jobs is a standard approach and added a reference 
that explores this aspect.

@@

Right, this comes from a previous version, thanks for pointing this out. 
We completed the reference: "Tuning Backfilling Queues" JSSPP17.
\medskip

@@

Right, we added an explanation for this in Section 6.1.3, page 8. This is due to the fact
that the resampling technique generates stationary data.\\

\textbf{Altogether, the reviewer believes that an experimental study with so
many design problems is not relevant to the readers of TDPS. }
\textbf{The reviewer does not see how the authors can overcome these
shortcomings even in a major revision and therefore suggest rejection of the
manuscript.}

We disagree. We strongly believe that such a unusual approach is valuable,
in the sense that it allows to get a sense of how useful simulators really are
for the purpose of tuning backfilling heuristics.\\

@@

Right, we polished the abstract accordingly\\

\textbf{Previous publications explain that studies using traces suffer from
fill-ins in the starting period and from draining in the final period. The
authors mention this problem but do not discuss their impact and strategies to
avoid these problems although other publications present such strategies.}

The use of our resampling method means the utilization is slightly lowered in
the experiments comparing to the original traces. We do not believe this to be
an issue, since we are studying adaptive methods in themselves, and not the 
underlying systems.\\

\textbf{Previous studies have described that the KTH trace is hardly comparable with
other traces due to a specific acceptance policy. The authors do not discuss
this problem.}

The traces we selected are quite disparate. This is on purpose to demonstrate
the value of an adaptive approach: it works well on any kind of system.
Moreover, our simulation model is simple: on real machines, we could reasonably
expect the difference in behavior to increase. (See the answer to reviewer 3
on this point.)\\

\textbf{The authors use either 1 week or 1 day feedback justifying their
choices with the periodicity of the traces. Although such approach is
reasonable, it is a hypothesis and requires validation by using other feedback
periods as well and comparing the results. }

We didn't set out to optimize the $\Delta$ hyperparameter. While we agree it
could be optimized further similarly to $\epsilon$ by leave-one-out
cross-validation, we don't believe it would add much to the discussion.\\

@@

Right. We modified the introduction to better reflect the scope of the study.
(See the last paragraph)\\

@@

We added two figures to illustrate the algorithms in page 7 and 8.\\

\textbf{Since the journal provides a platform for supplemental material, the
reviewer does not understand why readers must contact the authors by email to
obtain data to reproduce the study.}

As previously concerning the missing reference, this was inadvertent on our
part! This is fixed in the major revision. 
Thanks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Thanks!

@@

The need for more careful framing of the goals of the study was stressed by all
reviewers. Accordingly, we made the scope of the study more clear and changed
the title, to "Online Tuning of EASY-Backfilling using Queue Reordering
Policies."
\medskip

@@

\end{enumerate}
Thank you for your suggestions. These papers are indeed very related to our study. 
They have been included in the references.

@@

Right, we clarified this by adding a sentence describing principles of the algorithms.
\medskip

\textbf{Section 3.1 notation - intuitively p could represent processors just as
well as processing time, so I would suggest $t_i$ for time and $p_i$ for
processors.  Similarly, in Section 4.1 I for one would find the names more
intuitive with SJF/LJF instead of SPF/LPF (shortest/longest job first) SPF/LPF
instead of SQF/LQF (smallest/largest processors first) expansion factor is
often called slowdown area is often called total resources}

Well, our notations are coherent within the whole paper.
We agree that $p_i$ may be confusing for some readers.
However, since we lack of a standard, we chose
to use the classical notation of scheduling theory. 
Regarding the way to name the policies, they are different acronyms used in the literature,
again we chose to be consistent with the $p_i$ and $q_i$ notations - SPF corresponds to the
smallest $p_i$ first and SQF refers to the smallest $q_i$ first.  We added the remark
concerning the total resources and the expansion factor. This notation comes
from the "Characterization of backfilling strategies for parallel job
scheduling" paper, where the authors call \textit{Expansion Factor} the value of the
slowdown where the upper bound on the running-time is used. 
\medskip

@@

We agree that this design choice can be discussed. Our decision to divide
makes the study more realistic with respect to the cases where simulations are
expensive (which is the case for most large systems).  Indeed, the more realistic simulations, 
the larger time they take. For example, precise simulation frameworks such
as SimGrid/Batsim have large runtimes, and simulating the history of the whole
system every period is too prohibitive if the network topology and/or multiple
resource constraints are used. As for discounting - it can indeed be used
in both cases.
\medskip

@@

We agree that this does not change the estimate - the point of adding 
this noise was to show that the sample size is not prohibitive in practice.
Indeed, we learn the policy almost as fast with this noise, which
motivates the use of the technique in real-world cases. The main motivation for introducing this noise
was really to compare the difference in the shapes of the two green curves
in Figure 3.
\medskip

@@

You are right, we clarified this point in the text (SECTION xx - PAGE xx).\\

@@

Doing this would drown the point in the author's opinion. 
QUE VEUX-TU DIRE VRAIMENT ICI?
Good remark, we agree it is an interesting point, which was addressed in our previous publication 'Tuning
Backfilling Queues' (JSSPP17).
\medskip

  \textbf{Section 6.3.2 FCFS vs. Random: you justify the result be a conjecture that jobs do not pile up in the queue.  
  You should verify this by counting the jobs int he queue in the simulation.}

We agree that this conjecture is not warranted, and thus, we removed it in the revision.
We have plans to explore this aspect in a future work where the
discussion would be more appropriate.
\medskip

@@

Done, thanks you for the suggestion.
\medskip

@@

We changed the experimental protocol to use leave-one-out cross validation,
which did improve the bandit results. The selected exploration rate was 0.1 for
all traces, although it is not the best choice for all of them. (see the new
Table 2) The choice of a fixed exploration rate is one of simplicity - while
decaying exploration does provide better performance, it is also harder to
tune.
\medskip

@@

Right, this is corrected in the major revision. The reference is 'Tuning Backfilling Queues' (JSSPP17)
and it has been added in the references.
\medskip

@@

We incorporated all the suggested changes, thanks.
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Right, we agree that in order to really motivate the use of
bandit/resimulation approaches, one should compare the performance of static
policies, say using leave-one-trace-out cross validation, to the performance of
the adaptive variants, using leave-one-trace-out cross validation for their
hyperparameters.
However, this work does not aim to emphasize the necessity of the bandit
approach (the title has been changed and the introduction has been modified in the 
revision to better reflect this). Our goal was rather to show its advantages,
feasibility and limitations. 
There are two main reasons for not trying to be too demonstrative of the superiority
of the adaptive approach using our hypotheses, namely:

(1) First, this study used a limited amount of workload logs. In consequence, the
process of comparing the adaptive (hyperparameter-cross-validated) choice to
the static (cross-validated in the set of fixed policies) choice would not be
really conclusive.  Indeed, the more the number of workload logs, the higher the
diversity and the more adaptations are needed.

(2) Second, we used a light simulation model. In this model, we do make
machines *more* similar to each other by neglecting topological differences. It
can be reasonably expected that differences between systems should *increase*
rather than decrease, when moving away from a simplistic model to the real
systems.
We modified the present experiments to use leave-one-out cross
validation in the hyperparameter selection, and we clarified the reasons for
chosing this experimental protocol.
We are preparing a subsequent study using an approach closer to what you
describe, in which we greatly increase the number of workload logs used.
\medskip

\textbf{The authors assume +/-20 \% noise in the simulation running in the
proposed strategy. However, the reason why this assumption is suitable is not
presented. The authors should discuss the noise of 20 \% is suitable to represent
real world jobs.}

Right, a justification was clearly missing, this value is taken as to be
sufficiently larger than the values previously reported, see e.g. "Batsim: a
Realistic Language-Independent Resources and Jobs Management Systems Simulator"
which reports few percents of variation of the simulated metric compared to the
metric on the real systems. We added this remark in the text.\\

@@

Thanks, we incorporated all the corresponding changes in the text.
